---
title: 'Day 4'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Task description
We are given a file containing passport information. Each passport is represented by having `key:value` attributes sepparated by space or newline, while each passport is sepparated by a blankline. We are to count the #valid passports i.e. who have all of the following attributes:

* byr (Birth Year)
* iyr (Issue Year)
* eyr (Expiration Year)
* hgt (Height)
* hcl (Hair Color)
* ecl (Eye Color)
* pid (Passport ID)
* cid (Country ID) (this one is optional and hence not checked)

## Task solution
```{r}
#Prepare input data
file_name <- "input_file_4.txt"
input_file <- read_lines(file_name)


```
```{r}
valid <- 0
curr_attribs <- c()
#attrib_list <- c("byr:", "iyr:", "eyr:", "hgt:", "hcl:", "ecl:", "pid:")
attrib_list <- "(byr:|iyr:|eyr:|hgt:|hcl:|ecl:|pid:)"
n_attribs <- 7

#Checker for testing if the input contains elements of all_attribs
check_attrib <- function(str){
  str_extract_all(str, attrib_list, simplify = TRUE)
}

for (str in input_file) {
  if(str == "") {
    valid <- valid + ifelse((curr_attribs %>% length) == n_attribs, 1, 0)
    # print(c(curr_attribs, found_attribs,valid))
    curr_attribs <- c()
    next
  }
  curr_attribs <- c(curr_attribs,check_attrib(str))
}

#Adding 1 if the last passport was valid. (No "" to trigger after end of file)
valid + ifelse((curr_attribs %>% length) == n_attribs, 1, 0)
```



